NLIZE: A Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models

### 2018-07-23 paper/paper_entailVis.tex
add author list

% \documentclass[journal]{vgtc}                % final (journal style)
\documentclass[review,journal]{vgtc}         % review (journal style)
% \documentclass[review,journal]{vgtc}         % review (journal style)
%\documentclass[widereview]{vgtc}             % wide-spaced review
%\documentclass[preprint,journal]{vgtc}       % preprint (journal style)

@@

%% indicate IEEE Member or Student Member in form indicated below
% \author{Roy G. Biv, Ed Grimley, \textit{Member, IEEE}, and Martha Stewart}
% \authorfooter{
% %% insert punctuation at end of each item
% \item
%  Roy G. Biv is with Starbucks Research. E-mail: roy.g.biv@aol.com.
% \item
%  Ed Grimley is with Grimley Widgets, Inc.. E-mail: ed.grimley@aol.com.
% \item
%  Martha Stewart is with Martha Stewart Enterprises at Microsoft
%  Research. E-mail: martha.stewart@marthastewart.com.
% }

@@

%% Uncomment below to include a teaser figure.
% \teaser{
%   \centering
%   \includegraphics[width=\linewidth]{CypressView}
%   \caption{In the Clouds: Vancouver from Cypress Mountain. Note that the teaser may not be wider than the abstract block.}
% 	\label{fig:teaser}
% }
\teaser{
\vspace{-4mm}
 % \includegraphics[width=0.78\linewidth]{teaser}
 \includegraphics[width=1.0\linewidth]{teaser.pdf}
 \centering
 \vspace{-6mm}
  \caption{
The interface of the proposed system. During exploration, we can filter through a large number of sentence pairs summarized in (a). the current selected pair is displayed in (b). The model internal information (attention) is displayed in (d) and (e). The predicted probability (one of three labels: \emph{neural}, \emph{entailment}, \emph{contradiction}) is shown in the barycentric coordinate in (f). Finally, the high-level model structure and the updates to the model are summarized in (c).
}
% \vspace{-2mm}
\label{fig:teaser}
}

@@

%% if specified like this the section will be committed in review mode
\acknowledgments{
The authors wish to thank A, B, and C. This work was supported in part by
a grant from XYZ (\# 12345-67890).
}

>>>>

\documentclass[journal]{vgtc}                % final (journal style)
%\documentclass[review,journal]{vgtc}         % review (journal style)
% \documentclass[review,journal]{vgtc}         % review (journal style)
%\documentclass[widereview]{vgtc}             % wide-spaced review
%\documentclass[preprint,journal]{vgtc}       % preprint (journal style)

@@

%% indicate IEEE Member or Student Member in form indicated below
 \author{Shusen Liu, Zhimin Li, Tao Li, Vivek Srikumar, Valerio Pascucci, Peer-Timo Bremer}
 \authorfooter{
 \vspace{-2mm}
% %% insert punctuation at end of each item
 \item
  Shusen Liu, Peer-Timo Bremer is with Lawrence Livermore National Laboratory. E-mail: \{liu42, bremer5\}@llnl.gov.
 \item
  Zhimin Li, Valerio Pascucci is with SCI Institute, University of Utah. E-mail: \{zhiminl, pascucci\}@sci.utah.edu.
  Tao Li, Vivek Srikumar is with School of Computing, University of Utah, E-mail:\{tli,svivek\}@cs.utah.edu
}

@@

%% Uncomment below to include a teaser figure.
% \teaser{
%   \centering
%   \includegraphics[width=\linewidth]{CypressView}
%   \caption{In the Clouds: Vancouver from Cypress Mountain. Note that the teaser may not be wider than the abstract block.}
% 	\label{fig:teaser}
% }
\teaser{
%\vspace{-4mm}
 % \includegraphics[width=0.78\linewidth]{teaser}
 \includegraphics[width=1.0\linewidth]{teaser.pdf}
 \centering
 \vspace{-6mm}
  \caption{
The interface of the proposed system. During exploration, we can filter through a large number of sentence pairs summarized in (a). the current selected pair is displayed in (b). The model internal information (attention) is displayed in (d) and (e). The predicted probability (one of three labels: \emph{neural}, \emph{entailment}, \emph{contradiction}) is shown in the barycentric coordinate in (f). Finally, the high-level model structure and the updates to the model are summarized in (c).
}
% \vspace{-2mm}
\label{fig:teaser}
}

@@

%% if specified like this the section will be committed in review mode
\acknowledgments{
This work was performed under the auspices of the U.S. Department of Energy by Lawrence Livermore National Laboratory under Contract DE-AC52-07NA27344. This work is also supported in part by NSF: CGV: Award:1314896, NSF:IIP Award :1602127 NSF:ACI:award 1649923, DOE/SciDAC DESC0007446, CCMSC DE-NA0002375, and PIPER: ER26142 DE-SC0010498. This material is based upon work supported by the Department of Energy, National Nuclear Security Administration, under Award Number(s) DE-NA0002375. }
